A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-04-08 faculty.tex
updates

\subsection{Letters}
This is a huge part of the tenure package. You will need to ask for letters from senior people in your area.  Someone who can vouch for your research, teaching, and services.

You will need 4-6 letters, however you will not be the one asking for these letters, but your department will. However you can suggest who to ask. Typically, there will be two list of letter writers: one list consists of people suggested by you and the other list has people suggested by the department (e.g., people who work in your field in your dept).

>>>>

\subsection{Letters}
This is a huge part of the tenure package. You will need letters from senior people in your area.  Someone who can vouch for your research, teaching, and services.

You will need 4--6 letters, however you will not be the one asking for these letters, but your department will. However you can suggest who to ask. Typically, there will be two list of letter writers: one list consists of people suggested by you and the other list has people suggested by the department (e.g., people who work in your field in your dept).
